Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-08 PaperVictor.tex
Revise Seccion de teoria

% !TeX spellcheck = en_US
\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\usepackage{braket}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaV}[1]{{\bf \em \color{orange}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

\section{Theory}\label{s:theory}

\notaL{Pon etiquetas a todo para poderlo referir}
For the analysis of the propagation of electromagnetic fields through
multilayer systems it is usual to employ the transfer matrix
method \notaL{reference} \cite{Pochi2005, Ariza2011} \notaV{Agregue dos referencias}. 
Assuming the system is 1D, with variations
only along the $z$ directions, and that the polarization of light is either
transverse electric (TE) or transverse magnetic (TM)\notaL{si no, la matriz
  sería de 4x4}, the
transfer matrix $M\left(z_{2},z_{1}\right)$ is
a 2x2 matrix that relates the components of the electric $E_{\| }$
and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
evaluated at $z_2$ to their value at $z_{1}$,
\begin{equation*}
\left(
\begin{array}{c}
E_{\|} \\
H_{\| }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\| } \\
H_{\| }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain and use $M$
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
for the numerically stable calculation of the reflectance of large
multilayer systems, as
proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
supplementary information. The
explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha
  }}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido necesario
  explicarlas, y no creo que sean importantes para el lector} \notaV{Tiene raz\'{o}, esto se debe diferenciar en la informacion suplementaria} are the elements
of the transfer matrix which transfer
the fields from its surface interface with vacuum at $z_0$ towards the
substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
of the reflected and transmitted fields, where we choose the $F$'s as electric
fields for (TE) polarization and magnetic fields
for transverse magnetic polarization (TM). The upper sign $-$ in
Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively.
The reflectance is given by
$R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
TM polarization.\notaL{En el cálculo, ¿tomaste las partes reales? No
  estaban en la fórmula} \notaV{Realmente inclu\'{i} la transmitancia solo por completez (no inclu\'{i} c\'{a}lculo alguno)} The complex refractive index of the porous
layers were obtained through the Bruggeman's effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

\notaL{Creo que esto debería estar más adelante:
  After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you like. The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}. The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.
} \notaV{De acuerdo}

>>>>

% !TeX spellcheck = en_US
\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\usepackage{braket}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaV}[1]{{\bf \em \color{green}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

\section{Numerical simulation} \label{s:theory}

\notaV{Propuesto por Dr. David, se omite "Theory"}

\notaL{Pon etiquetas a todo para poderlo referir}

\notaV{Parrafos reescritos por Dr. David}

In this paper, two techniques are developed to design 
multilayer photonic structures. In the first, the wavelength 
($\lambda _{j}$), at which the $j$-th period of the structure 
is designed, is modulated by an increasing function. This can 
be as simple or complex as you like. The proposed function was 
optimized with the Minuit module of PDL (Perl Data Language) \cite{minuit}. 
The other technique for proposing highly reflective structures 
over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each 
sub-mirror the dispersion relation is analyzed.

For the analysis of the propagation of electromagnetic fields 
through multilayer systems, we employ the transfer matrix 
method based on Puente-Díaz et al., formalism \cite{Puente2020}. 
In spite some equivalent formulations have been proposed to 
obtain the optical properties of multilayer systems 
\cite{Mochan1987,Ortiz2020,Chavez2020}, here we use a 
recently developed formalism for the numerically stable 
calculation of the reflectance of large multilayer systems. 
Briefly describing, 
we assume a 1D system with variations along the $z$ direction 
and consider an incident linearly polarized beam of light 
(either TE or TM polarization) that propagates throughout 
the structure. The reflectance and transmittance are given by 
$R=|r|^{2}$ and  $T=\beta \left\vert t\right\vert ^{2}$, respectively, with
\begin{equation}
	r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
	t=\frac{2Z_{\zeta
	}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $Z_0$ and $Z_s$ are the impedances of the vacuum 
and the substrate, respectively. $\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$ is choosen for 
TE polarization while $\beta=\text{Re}Z_{s}/ 
\text{Re}Z_{0}$ for TM polarization. The upper sign 
$-$ in Eq. (\ref{rBloch}) and the subscript 
$\zeta =s$ in Eq. (\ref{tBloch}) are chosen for 
the case of TE polarization, while the lower sign 
$+$ and the subscript $\zeta =0$ correspond to TM 
polarization. Furthermore, $M_{ij}$ are the elements
of the transfer matrix which relates
the electromagnetic fields of all interfaces in the structure through
\begin{equation}
	M=\frac{1}{Z^{+}-Z^{-}}\left( 
	\begin{array}{cc}
		Z^{+}\text{exp}\left( iKD\right) -Z^{-}\text{exp}\left( -iKD\right)  & 
		-2iZ^{+}Z^{-}\sin KD \\ 
		2i\sin KD & Z^{+}\text{exp}\left( -iKD\right) -Z^{-}\text{exp}\left(
		iKD\right) 
	\end{array}%
	\right) \text{.}  \label{MsBloch}
\end{equation}
In this case, $Z^{\pm }$ can be obtained as 
\begin{equation}
	Z^{\pm }=-\frac{\widetilde{M}_{12}}{\widetilde{M}_{11}-\Lambda _{\pm }}\text{,}  \label{ZBloch}
\end{equation}%
being 
\begin{equation}
	\Lambda _{-}=\frac{1}{2}\text{tr}\widetilde{M}\pm i\sqrt{1-\left( \text{tr}\widetilde{M}/2\right)
		^{2}}\text{,}  \label{LBloch}
\end{equation}%
where the sign that satisfies the relation $\left\vert \Lambda
_{-}\right\vert >1$, and $\Lambda _{+}=\Lambda _{-}^{-1}$ is chosen.
Moreover, tr corresponds to the trace and $\widetilde{M}_{ij}$ $\left( i,j=1,2\right) 
$ denote the elements of the usual transfer matrix $\widetilde{M}$ of the $N$-layer
system, that is, 
\begin{equation}
	\widetilde{M} =\Pi _{j=1}^{N}%
	\begin{bmatrix}
		\cos k_{j}d_{j} & iZ_{j}\sin k_{j}d_{j} \\ 
		iY_{j}\sin k_{j}d_{j} & \cos k_{j}d_{j}%
	\end{bmatrix}%
	,  \label{Mcoef}
\end{equation}%
where 
\begin{equation}
	k_{j}=\sqrt{\epsilon _{j}q^{2}-Q^{2}}  \label{kj}
\end{equation}%
is the normal component (to the interfaces) of the wave vector, $Z_{j}$ is
the corresponding surface impedance, $Y_{j}=1/Z_{j}$ is the surface
admittance, $\epsilon _{j}=n_{j}^{2}$ is the permitivity (for simplicity we
assumed all media were nonmagnetic, with permeability $\mu _{i}=1$), $%
q=\omega /c=2\pi /\lambda $ is the free-space wavenumber corresponding to
the wavelength $\lambda $ and 
\begin{equation}
	Q=n_{0}q\sin \theta _{i}  \label{Snell}
\end{equation}%
is the projection of wavevector onto the interfaces, 
which is conserved according to Snell's law, with 
$\theta _{i}$ the angle of incidence. The surface 
impedances are given by $Z_{j}=q/k_{j}$ for TE 
polarization and $Z_{j}=k_{j}/q\epsilon _{j}$ for 
TM polarization. Moreover, sub-index $0$ and $s$ 
refer to the incident and substrate media, respectively.
The complex refractive index of the porous layers were 
obtained through the Bruggeman's effective medium 
theory, which has been reported to adequately reproduce 
the PS optical parameters \cite{Giusseppe2011,Pap2006,Estrada2018}.

\notaV{Se omite "For the analysis of the propagation of 
electromagnetic fields through multilayer systems it is 
usual to employ the transfer matrix method \notaL{reference} 
\cite{Pochi2005, Ariza2011}. Assuming the system is 1D, with 
variations only along the $z$ directions, and that the 
polarization of light is either transverse electric (TE) or 
transverse magnetic (TM)\notaL{si no, la matriz   sería de 4x4}, 
the transfer matrix $M\left(z_{2},z_{1}\right)$ is a 2x2 matrix 
that relates the components of the electric $E_{\| }$ and 
magnetic  $H_{\|}$ fields parallel to the $xy$ plane evaluated 
at $z_2$ to their value at $z_{1}$,
\begin{equation*}
\left(
\begin{array}{c}
E_{\|} \\
H_{\| }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\| } \\
H_{\| }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain and use $M$ \cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism for the numerically stable calculation of the reflectance of large multilayer systems, as proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the supplementary information. The explicit expressions for the optical coefficients are: 
\begin{equation}
r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha
  }}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido 
necesario explicarlas, y no creo que sean importantes para 
el lector} are the elements of the transfer matrix which 
relates the electromagnetic fields of all interfaces in 
the structure through transfer the fields from its surface 
interface with vacuum at $z_0$ towards the substrate at $z_s$,
$Z_0$ is the surface impedance of vacuum and $Z_s$ is the 
surface impedance of the substrate, and we define $r=F_r/F_i$ 
and $t=F_t/F_i$ in terms of the reflected and transmitted 
fields, where we choose the $F$'s as electric fields for 
(TE) polarization and magnetic fields for transverse 
magnetic polarization (TM).  The upper sign $-$ in Eq. 
(\ref{rBloch}) and the subscript $\alpha =s$ in Eq. 
(\ref{tBloch}) are chosen for the case of TE polarization, 
while the lower sign $+$ and the subscript $\zeta =0$ 
correspond to TM polarization, respectively. The reflectance 
is given by $R=|r|^{2}$ and the transmittance by 
$T=\beta \left\vert  t\right\vert ^{2}$ with 
$\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization 
and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for TM 
polarization.\notaL{En el cálculo, ¿tomaste las partes 
reales? No estaban en la fórmula} The complex refractive 
index of the porous layers were obtained through the 
Bruggeman's effective medium theory, which has been 
reported to adequately reproduce the PS optical 
parameters \cite{Giusseppe2011,Pap2006,Estrada2018}.}
